Active Learning : From Blackbox To Timed Connectors

### 2015-12-29 paper/paper.tex
.

Reo Coordination Model, obviously, is not a \emph{proper model} for learning.

So far as we can tell, most
works\cite{DBLP:conf/fase/RaffeltS06, DBLP:journals/corr/ChenHLLTWW15} on automata learning are not
capable of infinite models. \todo{reason?} Considering the semantics defined in section
\ref{sec:reo}, it's apparent that every finite connector has a corresponding constraint
automata, and the automata is also finite. Unfortunately, when checking the further definition of
Reo connectors' input, we find that it's not the case.

@@

\subsection{Parameterized Mealy Machine}
\begin{definition}[Parameterized Mealy Machine]
  A \emph{Parameterized Mealy Machine} is defined as a function $\mathcal{PM}(\Sigma)=\langle
  S(\Sigma), s_0, I, O, \delta(\Sigma), \lambda(\Sigma)\rangle$ that maps an
  alphabet to its corresponding Mealy Machine. 
  \begin{itemize}
    \item[-] $\Sigma$ is a \emph{finite} datum alphabet (hereafter referred to as an alphabet)
    \item[-] $S$ is a function that maps an alphabet to a \emph{finite} set of
      states. We use $S(\Sigma)$ to denote the state set.
    \item[-] $I$ is a finite set of source-ends.
    \item[-] $O$ is a finite set of sink-ends.
    \item[-] $s_0$ is the initial state. It satisfies $\forall \Sigma,s_0\in S(\Sigma)$
    \item[-] $\delta$ maps a \emph{finite} datum alphabet to an \emph{output function}. We use
      $\delta(\Sigma):S(\Sigma)\times Input(\Sigma,I)\rightarrow Output(\Sigma, O)$ to denote the output function.
    \item[-] $\lambda$ maps an alphabet to a \emph{transition function}. We use
      $\lambda(\Sigma):S(\Sigma)\times Input(\Sigma,I)\rightarrow S(\Sigma)$ to denote the transiton
      function.
  \end{itemize}
\end{definition}

In the definition above, \emph{Input} and \emph{Output} are used to generate input actions and output actions by the corresponding alphabets and ends.
\todo{How to say?}
\[
Input(\Sigma,I)=\{\}
\]
\[
Output(\Sigma,I)=\{\}
\]

@@

\todo{finish the definition ..}
\begin{definition}[Production of Parameterized Mealy Machines]
  Now we're going to define the production operator \emph{prod} of two parameterized mealy machines as,
  \[
  prod(PM_1,PM_2)=PM_3
  \]
  as follows. Here we assume that $PM_2.O\cap PM_1.I=\varnothing$
  \begin{itemize}
  	\item[-] $\forall\Sigma, PM_3.S(\Sigma)=PM_1.S(\Sigma)\times PM_2.S(\Sigma)$
    \item[-] $PM_3.I=PM_1.I\cup PM_2.I-PM_1.O$
    \item[-] $PM_3.O=PM_1.O\cup PM_2.O-PM_2.I$
    \item[-] $PM_3.s_0=(PM_1.s_0, PM_2.s_0)$
    \item[-] $\forall\Sigma, PM_3.\delta(\Sigma)((s_1,s_2), i)=$
      \begin{displaymath}
        \left\{
        \begin{array}[h]{ll}
          (Out_1 + Out_2)|_{PM_3.O} & \rblock\land Out_2\neq\rblock \\
          \rblock & otherwise \\
        \end{array}
        \right.
      \end{displaymath}
      where we have
      \begin{itemize}
        \item[*] $In_1 = i|_{PM_1.I}$
        \item[*] $Out_1 = PM_1.\delta(\Sigma)(s_1,In_1)$
        \item[*] $In_2 = (Out_1 + i)|_{PM_2.I}$
        \item[*] $Out_2 = PM_2.\delta(\Sigma)(s_2,In_2)$
      \end{itemize}
    \item[-] $\forall\Sigma, PM_3.\lambda(\Sigma)((s_1,s_2),i)=(s_1',s_2')$
      where we have
      \begin{itemize}
        \item[*] $s_1' = PM_1.\lambda(\Sigma)(s_1,In_1)$
        \item[*] $s_2' = PM_2.\lambda(\Sigma)(s_2,In_2)$
      \end{itemize}
  \end{itemize}
\end{definition}

\section{From Blackbox to Timed Connectors}
\subsection{Equivalence Query}
Generally, equivalence query has been proved impossible in blackbox
models\cite{DBLP:journals/iandc/Angluin87}. However, in this
section, we're showing that in certain circumstances, equivalence query can be implemented with
no approximation.

@@

\begin{definition}[Similar]
  In a mealy machine, two states are similar iff. they have the same output signature.
\end{definition}

>>>>

\subsection{External Behavior of Reo Connectors}
So far as we can tell, most
works\cite{DBLP:conf/fase/RaffeltS06, DBLP:journals/corr/ChenHLLTWW15} on automata learning are not
capable of infinite models. \todo{reason?} Considering the semantics defined in section
\ref{sec:reo}, it's apparent that every finite connector has a corresponding constraint
automata, and the automata is also finite. Unfortunately, when checking the further definition of
Reo connectors' input, we find that it's not the case.

@@

\subsection{Time Axis}
Time is involved in several extension of Reo like timed Reo, hybrid Reo, etc.\todo{citations}
Generally, these models are designed to handle real-time behavior where time is defined in
$\mathbb{R}$. However, we also found a lot of works where authors use rational time to make things
easier\todo{citations}.

\subsection{Parameterized Mealy Machine}
We present a model named \emph{parameterized mealy machine} to represent timed connectors. This
model is supposed to behave as a middle representation. Connectors are defined as parameterized
mealy machines, and composed via its production operator. Then original mealy-machine model will be
taken as semantics of PMM model.

\begin{definition}[Parameterized Mealy Machine]
  A \emph{Parameterized Mealy Machine} is defined as a function $\mathcal{PM}(\Sigma)=\langle
  S(\Sigma), s_0, I, O, \delta(\Sigma), \lambda(\Sigma)\rangle$ that maps an
  alphabet to its corresponding Mealy Machine. 
  \begin{itemize}
    \item[-] $\Sigma$ is a \emph{finite} datum alphabet (hereafter referred to as an alphabet)
    \item[-] $S$ is a function that maps an alphabet to a \emph{finite} set of
      states. We use $S(\Sigma)$ to denote the state set.
    \item[-] $I$ is a finite set of source-ends.
    \item[-] $O$ is a finite set of sink-ends.
    \item[-] $s_0$ is the initial state. It satisfies $\forall \Sigma,s_0\in S(\Sigma)$
    \item[-] $\delta$ maps a \emph{finite} datum alphabet to an \emph{output function}. We use
      $\delta(\Sigma):S(\Sigma)\times Input(\Sigma,I)\rightarrow Output(\Sigma, O)$ to denote the output function.
    \item[-] $\lambda$ maps an alphabet to a \emph{transition function}. We use
      $\lambda(\Sigma):S(\Sigma)\times Input(\Sigma,I)\rightarrow S(\Sigma)$ to denote the transiton
      function.
  \end{itemize}
\end{definition}

In the definition above, \emph{Input} and \emph{Output} are used to generate input actions and output actions by the corresponding alphabets and ends.
\todo{How to say?}
\[
Input(\Sigma,I)=\{\}\cup\{T\}
\]
where we use $T$ to denote the time action.
\[
Output(\Sigma,I)=\{\}
\]

@@

\begin{definition}[Production of Parameterized Mealy Machines]
  Now we're going to define the production operator \emph{prod} of two parameterized mealy machines as,
  \[
  prod(PM_1,PM_2)=PM_3
  \]
  as follows. Here we assume that $PM_2.O\cap PM_1.I=\varnothing$
  \begin{itemize}
  	\item[-] $\forall\Sigma, PM_3.S(\Sigma)=PM_1.S(\Sigma)\times PM_2.S(\Sigma)$
    \item[-] $PM_3.I=PM_1.I\cup PM_2.I-PM_1.O$
    \item[-] $PM_3.O=PM_1.O\cup PM_2.O-PM_2.I$
    \item[-] $PM_3.s_0=(PM_1.s_0, PM_2.s_0)$
    \item[-] $\forall\Sigma, PM_3.\delta(\Sigma)((s_1,s_2), i)=$
      \begin{displaymath}
        \left\{
        \begin{array}[h]{ll}
          (Out_1 + Out_2)|_{PM_3.O} & \rblock\land Out_2\neq\rblock \\
          \rblock & otherwise \\
        \end{array}
        \right.
      \end{displaymath}
      where we have
      \begin{itemize}
        \item[*] $In_1 = i|_{PM_1.I}$
        \item[*] $Out_1 = PM_1.\delta(\Sigma)(s_1,In_1)$
        \item[*] $In_2 = (Out_1 + i)|_{PM_2.I}$
        \item[*] $Out_2 = PM_2.\delta(\Sigma)(s_2,In_2)$
      \end{itemize}
    \item[-] $\forall\Sigma, PM_3.\lambda(\Sigma)((s_1,s_2),i)=(s_1',s_2')$
      where we have
      \begin{itemize}
        \item[*] $s_1' = PM_1.\lambda(\Sigma)(s_1,In_1)$
        \item[*] $s_2' = PM_2.\lambda(\Sigma)(s_2,In_2)$
      \end{itemize}
  \end{itemize}
\end{definition}

\section{From Blackbox to Timed Connectors}
\subsection{Adapted L* Algorithm}
\subsection{Equivalence Query}
Generally, equivalence query has been proved impossible in blackbox
models\cite{DBLP:journals/iandc/Angluin87}. However, in this
section, we're showing that in certain circumstances, equivalence query can be implemented with
no approximation.

@@

We say if two states are \emph{similiar} iff. they have the same output signature.
